### 2020-12-13 Thesis-Abstract.tex
Editorial improvements

Public debate has resumed on the topic of exceptional access (EA), which is alternative means of decryption intended for
law enforcement use. The resumption of this debate is not a renege on a resolute promise made at the end of the 1990s
``crypto war''; rather, it represents a valid reassessment of optimal policy in light of changing circumstances. The
imbalance between privacy, access, and security in the context of constantly changing society and technology is a wicked
problem that has and will continue to evade a permanent solution. As policymakers consider next steps, it is necessary
that the technical community to remain engaged. Although the introduction of EA would inevitably add risk, the quality
of the technical and regulatory approach can make a substantial difference. Furthermore, if one considers hard-line
legislative action and malicious abuse of cryptosystems as part of the threat model, well-designed EA may reduce risk
overall.

>>>>

Public debate has resumed on the topic of exceptional access (EA), which refers to alternative means of decryption
intended for law enforcement use. The resumption of this debate is not a renege on a resolute promise made at the end of
the 1990s ``crypto war''; rather, it represents a valid reassessment of optimal policy in light of changing
circumstances. The imbalance between privacy, access, and security in the context of constantly changing society and
technology is a wicked problem that has and will continue to evade a permanent solution. As policymakers consider next
steps, it is necessary that the technical community remain engaged. Although any EA framework would increase risk, the
magnitude of that increase varies greatly with the quality of the technical and regulatory approach. Furthermore, if one
considers hard-line legislative action and malicious abuse of cryptosystems as part of the threat model, well-designed
EA may reduce risk overall.

### 2020-12-13 Thesis-Chapter5-Arguments.tex
Editorial improvements

Despite its strength's \ac{lawful-hacking} is a sub-optimal compromise. Because it requires time and specialized skills,
it is unuseful for small departments and commonplace crimes. It would also alter the relationship between law
enforcement and tech companies. Law enforcement agencies would be forced into competition with tech companies if they
were incentivized to conceal the vulnerabilities they discover. Prominent proposals suggest mandating disclosure of
discovered vulnerabilities to mitigate this issue \cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016}.
Theoretically, the supply of vulnerabilities is very large, so even though the disclosed vulnerabilities would be
disclosed and patched, new ones could be found at a rate that maintains law enforcement access. Government could source
these vulnerabilities from a combination of the public domain, the commercial exploit market, and a central
``Vulnerability Lab'' \cite{bellovin_lawful_2013}.

The availability and cost of exploits fluctuates. For example, in January 2019, an Apple iOS jailbreak bug was valued at
\$2 million on the exploit market \cite{goodin_zeroday_2019}. In contrast, a 2020 report revealed that cracking mobile
devices cost law enforcement a mere \$2000 per unit \cite{koepke_2020}. As the exploit arms race continues,
exploitability will be inconsistent. In the end, law enforcement would face periods where it struggles for access, and
would need to develop costly exploits in the lab. Mandatory vulnerability disclosure is necessary to avoid competition
between law enforcement and tech companies. However, based on the \ac{FBI}'s historical abuses of power
\cite{shamsi_2011} and Congress's reluctance to fund initiatives it has passed \cite{keller_internet_2019} and failure
to provide strong oversight \cite{johnson_congressional_2004}, it seems unlikely that government would readily forfeit
expensive vulnerabilities.

@@

One class of \ac{DIM} \ac{EA} involves using strong cryptography, but including cryptographic puzzle pieces as message
metadata. These pieces are designed to reveal the encryption key after the surveiller spends considerable computational
power \cite{bellare_translucent_1996} \cite{wright_crypto_2018}. This approach precludes \ii{mass} surveillance, but it
also enables \ii{arbitrary} surveillance by anyone with enough computing power. Use in common cases would be impractical
due to high cost, but use in high profile cases would be less effective due to the likelihood of \ac{EA} workarounds
employed by sophisticated adversaries. Additionally, the calibration of puzzle difficulty is dependent on the state of
computing. Since opponents can record data and decrypt it later when computational capabilities have changed, the data
becomes steadily less secure over time.

Another \ac{DIM} proposal is to ``conference call'' authorities in as a ghost participant in the conversation. It was
notably suggested by \ac{GCHQ} officials Ian Levy and Crispin Robinson \cite{levy_robinson_2018}. Their writeup begins
with some core ideas of this thesis:

@@

As goodwill participants in the conversation, trying to spur discussion around specific proposals ``without people being
vilified for having a point of view or daring to work on this as a problem,'' they deserve credit and thanks.

Unfortunately, the proposal they share is indeed problematic. The ghost user proposal prides itself on not compromising
strong encryption. This is a good property, but compromising a messaging app's authorization protocol is as dangerous as
compromising its encryption \cite{callas_1_2019}. Fundamentally, it suffers from the same weakness as trusted-party key
escrow; the introduction of an authorization vulnerability in the messaging service provider's platform amounts to a
highly risky centralized access capability \cite{schneier_ghost_2019}. It has the same nature, if a different form, as
rejected key escrow proposals.

Finally, one \ac{DAR}-specific \ac{EA} class is device key escrow. In this scheme, key recovery material exists on the
device itself. While not necessary to classify as device key escrow, most of these proposals include physical possession
requirements and additionally ``brick'' the device or make it absolutely clear that \ac{EA} has been performed
\cite{savage_lawful_2018} \cite{ozzie_2018}. Such features preclude \ac{masssurv} and ensure transparency to the device
user. This approach relies on secure hardware and a method of authorizing the recovery request to the device itself. The
authentication step can be paired with other \ac{EA} strategies, such as engaging with trusted-parties or distributed
systems. This is where the device escrow shows its weaknesses. Secure hardware enclaves, though improving, are not
totally reliable, and authentication to the hardware device is susceptible to the same attacks as traditional escrow
\ac{EA}.

Device key escrow's greatest weaknesses, however, still represent signs of progress. It is true that it relies on a
device's secure enclave, but devices already do---it is the same hardware device that manages device unlock and
encryption functionality in the first place. Adding functionality increases the attack surface, but it does not add a
completely new threat vector. It is also true that the process is subject to the same problems as traditional key escrow
after the device has been obtained, but that is precisely the progress that has been made---\ii{after the device has
been obtained}. Leveraging advances in secure hardware design has meaningfully changed the \ac{EA} risk profile.

In 2019, Carnegie Mellon assembled an ideologically diverse group of policy and security experts to engage in the kind
of cross-disciplinary debate this thesis advocates. After considering all the technical corners of the situation, their
report goes into detail on why \ac{EA} for domestic law enforcement (i.e., common cases instead of sophisticated
adversaries) focusing on \ac{DAR} in mobile phones using device key escrow requiring physical access is the most
tractable technical niche to consider \cite{group_2019}. By now it should be clear why: traditional investigation mixed
with a dose of lawful hacking is best suited for advanced opponents, and device key escrow represents actual progress as
a path towards lower-risk \ac{EA} for typical cases.

>>>>

Despite its strengths \ac{lawful-hacking} is a sub-optimal compromise. Because it requires time and specialized skills,
it is not useful for small departments and commonplace crimes. It would also alter the relationship between law
enforcement and tech companies. Law enforcement agencies would be forced into competition with tech companies if they
were incentivized to conceal the vulnerabilities they discover. Prominent proposals suggest mandating disclosure of
discovered vulnerabilities to mitigate this issue \cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016}.
Theoretically, there are enough vulnerabilities that, even though these discovered vulnerabilities would be disclosed and
patched, new ones could be found quickly enough to enable steady levels of access. Government could source these
vulnerabilities from a combination of the public domain, the commercial exploit market, and a central ``Vulnerability
Lab'' \cite{bellovin_lawful_2013}.

The availability and cost of exploits fluctuates. For example, in January 2019, an Apple iOS jailbreak bug was valued at
\$2 million on the exploit market \cite{goodin_zeroday_2019}. In contrast, a 2020 report revealed that cracking mobile
devices cost law enforcement a mere \$2000 per unit \cite{koepke_2020}. As the exploit arms race continues,
exploitability will be inconsistent. If law enforcement relies on \ac{lawful-hacking} as its strategy, it would face
periods where it struggles for access, and would need to develop costly exploits in the lab. Mandatory vulnerability
disclosure is necessary to avoid competition between law enforcement and tech companies. However, based on the
\ac{FBI}'s historical abuses of power \cite{shamsi_2011} and Congress's reluctance to fund initiatives it has passed
\cite{keller_internet_2019} and failure to provide strong oversight \cite{johnson_congressional_2004}, it seems unlikely
that government would readily forfeit expensive vulnerabilities.

@@

One class of \ac{DIM} \ac{EA} involves using strong cryptography, but including cryptographic puzzle pieces as message
metadata. These pieces are designed to reveal the encryption key after the surveiller spends considerable computational
power \cite{bellare_translucent_1996} \cite{wright_crypto_2018}. This approach precludes mass surveillance, but it also
enables arbitrary surveillance by anyone with enough computing power. Using this class of \ac{DIM} \ac{EA} in common
cases would be impractical due to its high cost. However, it would be less effective in high-profile cases due to the
ability of sophisticated adversaries to employ \ac{EA} workarounds. Additionally, the calibration of puzzle difficulty
is dependent on the state of computing. Since opponents can record data and decrypt it later when computational
capabilities have changed, the data becomes steadily less secure over time.

Another \ac{DIM} proposal is to ``conference call'' authorities in as ghost participants in the conversation. This was
notably suggested by \ac{GCHQ} officials Ian Levy and Crispin Robinson \cite{levy_robinson_2018}. Their writeup begins
with some core ideas of this thesis:

@@

Although this proposal was raised with good intentions, it is nevertheless problematic. The ghost user proposal prides
itself on not compromising strong encryption. Although this is a good property, compromising a messaging app's
authorization protocol is as dangerous as compromising its encryption \cite{callas_1_2019}. Fundamentally, this proposal
suffers from the same weakness as trusted-party key escrow---it introduces an authorization vulnerability in the
messaging service provider's platform, resulting in dangerous centralized access capability \cite{schneier_ghost_2019}.
It has the same nature, if a different form, as rejected key escrow proposals.

Finally, one \ac{DAR}-specific \ac{EA} class is device key escrow. In this scheme, key recovery material exists on the
device itself. While not necessary to classify as device key escrow, most of these proposals include physical possession
requirements and additionally ``brick'' the device or make it absolutely clear that \ac{EA} has been performed
\cite{savage_lawful_2018} \cite{ozzie_2018}. Such features preclude \ac{masssurv} and ensure transparency to the device
user. This approach relies on secure hardware and a method of authorizing the recovery request to the device itself. The
authentication step can be paired with other \ac{EA} strategies, such as engaging with trusted-parties or distributed
systems. This is where the weakness of the device escrow is revealed. Secure hardware enclaves, though improving, are
not totally reliable. Therefore, authentication to the hardware device is susceptible to the same attacks as traditional
escrow \ac{EA}.

Device key escrow's greatest weaknesses, however, are still signs of progress. It is true that it relies on a device's
secure enclave, but devices already do---it is the same hardware device that manages device unlock and encryption
functionality in the first place. Additional functionality increases the attack surface, but it does not add a
completely new threat vector. It is also true that the process is subject to the same problems as traditional key escrow
after the device has been obtained, but that is precisely the progress that has been made---\ii{after the device has
been obtained}. Advances in secure hardware design have meaningfully changed the \ac{EA} risk profile.

In 2019, Carnegie Mellon assembled an ideologically diverse group of policy and security experts to engage in the kind
of cross-disciplinary research. After describing every technical branch of the situation, their report goes into detail
on why \ac{EA} for domestic law enforcement (i.e., common cases instead of sophisticated adversaries) focusing on
\ac{DAR} in mobile phones using device key escrow requiring physical access is the most tractable technical niche to
consider \cite{group_2019}. By now it should be clear why: traditional investigation mixed with a dose of lawful hacking
is best suited for advanced opponents, and device key escrow represents actual progress as a path towards lower-risk
\ac{EA} for typical cases.

### 2020-12-13 Thesis-Chapter6-ThreatModel.tex
Work on DFD section and normalize captions
Editorial improvements

This chapter consists of a threat model and analysis of a specific device key escrow \ac{EA} proposal, Stefan Savage's
``Lawful Device Access without Mass Surveillance Risk: A Technical Design Discussion'' \cite{savage_lawful_2018}. The
proposal is specific to \acl{DAR} for mobile devices. Lacking a concise name, this proposal will be referred to by its
acronym, \ldawmsR. This chapter assumes that the proposal is accompanied by some legal framework regulating its
application and use, though it is not the focus of this analysis, and nothing is assumed about it in particular. Note
that the creators of the proposal intentionally chose the phrase ``lawful access'' over ``\acl{EA}'' in order to
emphasize the role of legal process and dispel the negative stigma that accompanies \ac{EA}. I refer to \ldawmsr as an
\ac{EA} proposal, but use the term entirely in the spirit of their paper.

@@

The essential threat modeling questions are ``what are we building'' and ``what can go wrong.'' The first step to
answering those questions is to establish goals for the former and a list of threats in anticipation of the latter. The
\ldawmsr proposal describes a threat model against which it was designed. This model takes cues from that one but is
intended to be more generally applicable for any \ac{DAR} \ac{EA} proposal.

@@

The goals of an \ac{EA} cryptosystem are taken from the metrics of \mychap{chap-arguments}. Their justification stems
from the preceding arguments. Each goal is listed according to priority, though none are absolute.

@@

\modelitem{Security}{The system should minimize increased security risk with reference to the current state of the art.
Risk is considered both with respect to individual devices and to the integrity of the entire class of devices.}

\modelitem{Protection of civil liberties}{The system should include measures to prevent \ac{masssurv} and abuse by
political regimes that violate civil rights. This includes technologically enforcing the fundamental right to privacy
but upon warranted search pursuant to the rule of law.}

\modelitem{Transparency}{The system should be auditable by the public to enable trust that this significant power is
being used responsibly. In the case of \ac{DAR}, the subject of the search should be aware of the access.}

\modelitem{Law enforcement utility}{The system should actually be useful to law enforcement in terms of reliability,
speed, and cost.}

\modelitem{Economic impact}{The system should consider global competitiveness of devices using the cryptosystem as well
as the distribution of costs associated with its development and administration. Even though this is a security-oriented
threat model, architectural decisions determine the system's economics, and economics determines the system's ultimate
feasibility.}

@@

\ac{EA} threat models necessarily include the full cast of traditional threat actors.

@@

\modelitem{Criminals: ordinary, organized, cyber}{Criminals represent a threat to the \ac{EA} system by trying to use it
to gain access without authority. Ordinary thieves may want to spy on a target or steal and resell phones. They will
have physical access but only simple tools, using ordinary device interfaces. Organized criminals will have the same
motives but considerably more advanced technical capabilities, exerting full control over all interfaces. Cyber
criminals have a wide spectrum of motivations and capabilities. Their significant contribution to the threat landscape
is that they will target the backend systems that operate the \ac{EA} system in order to steal and likely sell whatever
access capabilities they can find.}

\modelitem{Insider threat}{The insider threat is someone within the \ac{EA} recovery process, whether at the law
enforcement agency or a vendor, that seeks to abuse the system for their own purposes. They may represent the
motivations and capabilities of any of the criminal categories, but they begin with privileged access somewhere in the
process.}

\modelitem{Foreign intelligence}{Foreign intelligence agencies and \acp{APT} are always looking for means to escalate
access and tamper with and steal information. They have world-class expertise and computing power, which they will apply
to both individual devices and backend systems. (Here I am referring to \ii{foreign} foreign intelligence agencies, as
opposed to \ii{domestic} foreign intelligence agencies such as the \acs{CIA} or \acs{NSA} in the U.S., which are assumed
to operate within---though push the boundaries of---the legal framework.)}

\modelitem{Authoritarian regimes}{States that do not respect lawful process will try to compel administers of an \ac{EA}
system to provide access upon demand. Legal coercion may or may not be combined with state-backed hacking capability.}

@@

To make sense of an \ac{EA} proposal in the face of the stated goals and such a formidable list of threat actors, one
must include two non-traditional threats. To do so is to step back and look at the situation from a broader view than
security experts usually take.

@@

\modelitem{The platform abuser}{The device user may actually be a threat in the larger safety context. The end user is
not the most important thing. This is a crucial point.

All technologies have embedded values \cite{rogaway_moral_2015}, and at the top of this value system is some most
important ``thing.'' Traditional device security threat models make the end user the most important thing. This is a
very good rule. It leads to good security priorities and more importantly, honors the user's rights and autonomy.

To stray from this rule is dangerous, but---make no mistake---it is already done on a regular basis. Software that can
force updates values the vendor's judgement over the user's (even if it is a good idea). Software that enforces Digital
Rights Management values corporations' data rights over the user's (sometimes to extremes \cite{eff_2020}). Software
that doesn't encrypt user communications at all values the service provider's ability to scrape personal information to
create targeted ads over the user's privacy. Software that enables \ac{EA} values lawful investigatory process
over the user's ultimate privacy. Intentional subversion of the user's will is not a comfortable thought, but it is a
frequent reality, and the reality of \ac{EA}.

In the broader threat model, the platform abuser is someone who is using the device encryption for cover of illicit
activities. He represents a threat to public safety.}

\modelitem{Hawkish lawmakers}{If one's very highest priorities are security and privacy for society as a whole, then
aggressive lawmakers that have the power to \ii{mandate} arbitrary data access represent perhaps the largest threat of
all. Crypto-anarchists can encrypt their data above the compromised layer all they want, but the vast majority of
individuals using default products and all above-the-table organizations will abide by U.S. law.

Hawkish lawmakers are a threat to the security of a cryptosystem (using \ac{EA} or not) in that they may judge it too
inhibitive to law enforcement and outlaw its very use, mandating something weaker in its place.}

@@

The following considerations are out of scope for this threat model.

@@

\modelitem{\ac{EA} workarounds}{The user is capable of evading \ac{EA} mechanisms by encrypting data at a higher level
in the tech stack, e.g. by encrypting files before saving them to disk. Additionally, investigators or attackers are
frequently capable of bypassing current lockout mechanisms. These have already been discussed, and it out of scope for
evaluating the \ac{EA} system itself.}

\modelitem{Supply chain attacks}{Protecting device hardware and software supply chains is necessary to prevent
surreptitious, trivially exploitable backdoors. For the purposes of this threat model, device hardware and software are
considered to be as-intended, though they are assumed to contain the standard amount of bugs and side-channels.}

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone.png}
    \caption{The basic encrypted mobile phone data flow diagram.}
    \label{fig-dfd-iphone}
\end{figure}

@@

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=0.9\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR.png}
    \caption{The LDAWMSR data flow diagram.}
    \label{fig-dfd-ldawmsr}
\end{figure}

@@

\begin{figure}[H]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR-setup.png}
  \caption{The LDAWMSR maintenance data flow diagram.}
  \label{fig-dfd-ldawmsr-setup}
\end{figure}

>>>>

This chapter consists of a threat model and analysis of a specific device key escrow \ac{EA} proposal, Stefan Savage's
``Lawful Device Access without Mass Surveillance Risk: A Technical Design Discussion'' \cite{savage_lawful_2018}. The
proposal is specific to \acl{DAR} for mobile devices. Due to the length of its title, this proposal will be referred to
by its acronym, \ldawmsR. This chapter assumes that the proposal is accompanied by some legal framework regulating its
application and use, though it is not the focus of this analysis, and nothing is assumed about it in particular. Note
that the creators of the proposal intentionally chose the phrase ``lawful access'' over ``\acl{EA}'' in order to
emphasize the role of legal process and dispel the negative stigma that accompanies \ac{EA}. I refer to \ldawmsr as an
\ac{EA} proposal, but use the term in the spirit of their paper.

@@

``What are we building?'' and ``What can go wrong?'' are the essential threat modeling questions. The first step to
answering those questions is to establish goals for the former and a list of threats in anticipation of the latter. The
\ldawmsr proposal describes a threat model against which it was designed. This model takes cues from that one but is
intended to be more generally applicable for any \ac{DAR} \ac{EA} proposal.

@@

The goals of an \ac{EA} cryptosystem are taken from the metrics of \mychap{chap-arguments}. Their justification stems
from the preceding arguments. Each goal is listed according to priority, though no goal has absolute priority over the
others.

@@

\modelitem{Security}{The system should minimize security risk with reference to the current state of the art. Risk is
considered with respect to both individual devices and the entire class of devices.}

\modelitem{Protection of civil liberties}{The system should include measures to prevent \ac{masssurv} and abuse by
authoritarian regimes. This includes technologically enforcing the fundamental right to privacy but upon warranted
search pursuant to the rule of law.}

\modelitem{Transparency}{The system should be auditable by the public to enable verification that its power is being
used responsibly. In the case of \ac{DAR}, the subject of the search should be aware of the access.}

\modelitem{Law enforcement utility}{The system should be useful to law enforcement in terms of reliability, speed, and
cost.}

\modelitem{Economic impact}{The system should consider global competitiveness of devices using the cryptosystem and the
distribution of costs associated with its development and administration. Even though this is a security-oriented threat
model, architectural decisions determine the system's economics, and economics determines the system's ultimate
feasibility.}

@@

\ac{EA} threat models include the full cast of traditional threat actors.

@@

\modelitem{Criminals: ordinary, organized, cyber}{Criminals threaten the \ac{EA} system by using it to access plaintext
without authority. Ordinary thieves may spy on targets or steal and resell phones. They will have physical
access but only simple tools that use ordinary device interfaces. Organized criminals will have the same motives but
considerably more advanced technical capabilities, exerting full control over all interfaces. Cyber criminals have a
wide spectrum of motivations and capabilities. Their significant contribution to the threat landscape is that they will
target the backend systems that operate the \ac{EA} system in order to steal and likely sell whatever access
capabilities they can find.}

\modelitem{Insider threat}{The insider threat involves someone within the \ac{EA} recovery process, perhaps at the law
enforcement agency or a vendor, that seeks to abuse the system for their own purposes. They may have the same
motivations and skills of any other criminal category, but they have the advantage of privileged access at some stage in
the process.}

\modelitem{Foreign intelligence}{Foreign intelligence agencies and \acp{APT} are constantly looking for ways to escalate
privilege and tamper with or steal information. They have world-class expertise and computing power, which they can
apply to both individual devices and backend systems. (Here I am referring to \ii{foreign} foreign intelligence
agencies, as opposed to \ii{domestic} foreign intelligence agencies such as the \acs{CIA} or \acs{NSA} in the U.S.,
which are assumed to operate within---though push the boundaries of---the legal framework.)}

\modelitem{Authoritarian regimes}{States that do not respect lawful process will try to compel administrators of an
\ac{EA} system to provide access upon demand. Legal coercion may or may not be combined with state-backed hacking
capability.}

@@

To make sense of an \ac{EA} proposal in the face of the stated goals and such a formidable list of threat actors, one
must include two non-traditional threats. To do so is to step back and view the situation with a broader perspective
than security experts usually take.

@@

\modelitem{The platform abuser}{The device user him or herself may actually be a threat in the larger safety context.
The end user is not the most important thing. This is a crucial point.

All technologies have embedded values \cite{rogaway_moral_2015}, and at the top of this value system is some most
important ``thing.'' Traditional device security threat models define this ``thing'' as the end user. This leads to good
security priorities and honors the user's rights and autonomy.

To stray from this rule is dangerous, but is already frequent practice. Software that forces updates values the vendor's
judgement over the user's (even if it is a good idea). Software that enforces Digital Rights Management values
corporations' data rights over the user's (sometimes to extremes \cite{eff_2020}). Software that does not encrypt user
communications at all values the service provider's ability to scrape personal information over the user's privacy.
Software that enables \ac{EA} values lawful investigatory process over the user's ultimate privacy. Intentional
subversion of the user's will is not a comfortable thought, but it is a frequent reality, and the reality of \ac{EA}.

In the broader threat model, the platform abuser uses encryption to hide illicit activities. He is a threat to public
safety.}

\modelitem{Hawkish lawmakers}{If one's very highest priorities are security and privacy for society as a whole, then
aggressive lawmakers that have the power to \ii{mandate} arbitrary data access represent perhaps the largest threat of
all. Crypto-anarchists can encrypt their data above the compromised layer all they want, but above-the-table
organizations and most individuals who use default products will abide by U.S. law.

Hawkish lawmakers threaten the security of a cryptosystem (using \ac{EA} or not) because they may judge the system as
too inhibitive to law enforcement. Therefore, they may outlaw its use and mandate something weaker in its place.}

@@

The following considerations are beyond the scope of this threat model.

@@

\modelitem{\ac{EA} workarounds}{The user can evade \ac{EA} mechanisms by encrypting data at a higher level in the tech
stack, for example by encrypting files before saving them to disk. Additionally, investigators or attackers can often
bypass current lockout mechanisms. This has already been discussed, and is not relevant when evaluating the \ac{EA}
system itself.}

\modelitem{Supply chain attacks}{It is necessary to protecting device hardware and software supply chains in order to
prevent surreptitious, trivially exploitable backdoors. For the purposes of this threat model, device hardware and
software are considered to be as-intended, though they are assumed to contain the standard amount of bugs and
side-channels.}

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone.png}
    \caption{The basic encrypted mobile phone data flow diagram}
    \label{fig-dfd-iphone}
\end{figure}

@@

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=0.9\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR.png}
    \caption{The LDAWMSR data flow diagram}
    \label{fig-dfd-ldawmsr}
\end{figure}

@@

\begin{figure}[H]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR-setup.png}
  \caption{The LDAWMSR maintenance data flow diagram}
  \label{fig-dfd-ldawmsr-setup}
\end{figure}
